\bf Visual Inference for Significance and Goodness-of-Fit Testing for a Social Network Model

### 2017-11-02 ASApaper/paper-child.Rnw
some more formatting

<<getexperdetail, results='asis'>>=
turk22 <- read_csv("data/turk22-sig.csv")
modelData_sig <- turk22 %>% 
  mutate(type2 = ifelse(sign == 0, sign(initialEst), sign),
         type2 = ifelse(type == "one", type2, -1)) %>% 
  filter(pic_id != 3132) 
modelData_sig %>% group_by(test_param, type2, difficulty, size) %>%
  count() %>% ungroup() %>%
  spread(difficulty, size) -> step1
step1 %>% select(1:4) %>% filter(!is.na(`1`)) -> step2a
step1 %>% select(c(1:3,5)) %>% filter(!is.na(`2`)) -> step2b
step1 %>% select(c(1:3,6)) %>% filter(!is.na(`3`)) -> step2c
experdet <- step2a %>% mutate(easy = `1`, medium = step2b$`2`, hard = step2c$`3`) %>% select(-c(`1`, n))
experdet$test_param <- as.factor(experdet$test_param)
levels(experdet$test_param) <- paste0("beta", c(1,3,4,2,6,5))
experdet$test_param <- as.character(experdet$test_param)
names(experdet) <- c("Parameter", "Lineup Type", "Easy Value", "Medium Value", "Hard Value")

print(xtable::xtable(experdet, caption = "All conditions in our MTurk experiment. Note that for $\\beta_4$ and $\\beta_6$, the negative type experiments are the reverse lineups, where 5 plots were simulated from the model with the parameter value given in the table, while 1 plot was simulated from M1.", label = "tab:experdetail", digits = c(0,0,0,3,4,3)))
@

@@

<<glmmres>>=
load("data/finalglmm31-2.RDA")
mod <- model2randomscalesize
res <- summary(mod)[[10]]
ests <- as.numeric(round(res[,1], 4))
oddsidx <- which(exp(ests) < .0001)
oddsidx2 <- which(exp(ests) > 1000000)
odds <- round(exp(ests), 4)
odds[oddsidx] <- "$<$0.0001"
odds[oddsidx2] <- "$>$1e+06"
se <- as.numeric(round(res[,2], 4))
pvalidx <- which(res[,4] < .0001)
pval <- as.numeric(round(res[,4],4))
pval[pvalidx] <- "$<$0.0001"
sigma_epsilon <- summary(model2randomscalesize)[[13]]$nick_name[[1]]
sigma_delta <- summary(model2randomscalesize)[[13]]$pic_id[[1]]
@

\begin{table}
\centering
\begin{tabular}{lrrrr}
Parameter & Estimate & Std Error & $p$-value & Odds Multiplier \\
$\alpha_{1-1}$ & \Sexpr{ests[1]} & \Sexpr{se[1]} & \Sexpr{pval[1]} & \Sexpr{odds[1]}\\
$\alpha_{2-1}$ & \Sexpr{ests[2]} & \Sexpr{se[2]} & \Sexpr{pval[2]} & \Sexpr{odds[2]} \\
$\alpha_{3-1}$ & \Sexpr{ests[3]} & \Sexpr{se[3]} & \Sexpr{pval[3]} & \Sexpr{odds[3]}  \\
$\alpha_{4-1}$  & \Sexpr{ests[4]} & \Sexpr{se[4]} & \Sexpr{pval[4]} & \Sexpr{odds[4]} \\
$\alpha_{5-1}$ & \Sexpr{ests[5]} & \Sexpr{se[5]} & \Sexpr{pval[5]} & \Sexpr{odds[5]}  \\
$\alpha_{6-1}$  & \Sexpr{ests[6]} & \Sexpr{se[6]} & \Sexpr{pval[6]} & \Sexpr{odds[6]} \\
$\alpha_{11}$ & \Sexpr{ests[7]} & \Sexpr{se[7]} & \Sexpr{pval[7]} & \Sexpr{odds[7]} \\
$\alpha_{21}$  & \Sexpr{ests[8]} & \Sexpr{se[8]} & \Sexpr{pval[8]} & \Sexpr{odds[8]} \\ 
$\alpha_{31}$ & \Sexpr{ests[9]} & \Sexpr{se[9]} & \Sexpr{pval[9]} & \Sexpr{odds[9]} \\
$\alpha_{41}$  & \Sexpr{ests[10]} & \Sexpr{se[10]} & \Sexpr{pval[10]} & \Sexpr{odds[10]} \\
$\alpha_{51}$  & \Sexpr{ests[11]} & \Sexpr{se[11]} & \Sexpr{pval[11]} & \Sexpr{odds[11]} \\
$\alpha_{61}$  & \Sexpr{ests[12]} & \Sexpr{se[12]} & \Sexpr{pval[12]} & \Sexpr{odds[12]} \\
$\beta_{1-1}$  & \Sexpr{ests[13]} & \Sexpr{se[13]} & \Sexpr{pval[13]} & \Sexpr{odds[13]} \\
$\beta_{2-1}$   & \Sexpr{ests[14]} & \Sexpr{se[14]} & \Sexpr{pval[14]} & \Sexpr{odds[14]} \\
$\beta_{3-1}$  & \Sexpr{ests[15]} & \Sexpr{se[15]} & \Sexpr{pval[15]} & \Sexpr{odds[15]} \\
$\beta_{4-1}$  & \Sexpr{ests[16]} & \Sexpr{se[16]} & \Sexpr{pval[16]} & \Sexpr{odds[16]} \\
$\beta_{5-1}$ & \Sexpr{ests[17]} & \Sexpr{se[17]} & \Sexpr{pval[17]} & \Sexpr{odds[17]} \\
$\beta_{6-1}$ & \Sexpr{ests[18]} & \Sexpr{se[18]} & \Sexpr{pval[18]} & \Sexpr{odds[18]} \\
$\beta_{11}$ & \Sexpr{ests[19]} & \Sexpr{se[19]} & \Sexpr{pval[19]} & \Sexpr{odds[19]} \\
$\beta_{21}$ & \Sexpr{ests[20]} & \Sexpr{se[20]} & \Sexpr{pval[20]} & \Sexpr{odds[20]}  \\
$\beta_{31}$ & \Sexpr{ests[21]} & \Sexpr{se[21]} & \Sexpr{pval[21]} & \Sexpr{odds[21]} \\
$\beta_{41}$ & \Sexpr{ests[22]} & \Sexpr{se[22]} & \Sexpr{pval[22]} & \Sexpr{odds[22]} \\
$\beta_{51}$ & \Sexpr{ests[23]} & \Sexpr{se[23]} & \Sexpr{pval[23]} & \Sexpr{odds[23]} \\
$\beta_{61}$ & \Sexpr{ests[24]} & \Sexpr{se[24]} & \Sexpr{pval[24]} & \Sexpr{odds[24]} \\ 
$\sigma^2_{\delta}$ & \Sexpr{round(sigma_delta, 4)} & -- & -- & --\\
$\sigma^2_{\epsilon}$ &  \Sexpr{round(sigma_epsilon, 4)}  & -- & -- & --
\end{tabular}
\caption{\label{tab:glmmests}Summary of the results from fitting the model given in Equation~\ref{eq:glmm}}
\end{table}

>>>>

<<getexperdetail, results='asis'>>=
turk22 <- read_csv("data/turk22-sig.csv")
modelData_sig <- turk22 %>% 
  mutate(type2 = ifelse(sign == 0, sign(initialEst), sign),
         type2 = ifelse(type == "one", type2, -1)) %>% 
  filter(pic_id != 3132) 
modelData_sig %>% group_by(test_param, type2, difficulty, size) %>%
  count() %>% ungroup() %>%
  spread(difficulty, size) -> step1
step1 %>% select(1:4) %>% filter(!is.na(`1`)) -> step2a
step1 %>% select(c(1:3,5)) %>% filter(!is.na(`2`)) -> step2b
step1 %>% select(c(1:3,6)) %>% filter(!is.na(`3`)) -> step2c
experdet <- step2a %>% mutate(easy = `1`, medium = step2b$`2`, hard = step2c$`3`) %>% select(-c(`1`, n))
experdet$test_param <- as.factor(experdet$test_param)
levels(experdet$test_param) <- paste0("beta", c(1,3,4,2,6,5))
experdet$test_param <- factor(experdet$test_param, levels=paste0("beta", c(1,2,3,5,4,6)))
experdet <- experdet %>% arrange(test_param)
experdet$test_param <- as.character(experdet$test_param)
experdet$test_param[c(2,4,6,8,10,12)] <- NA
experdet$type2 <- c(rep(c("neg", "pos"), 4), rep(c("regular", "reverse"), 2))
names(experdet) <- c("Parameter", "Condition", "Easy Value", "Medium Value", "Hard Value")

print(xtable::xtable(experdet, caption = "All conditions used for the MTurk experiment. For parameters $\beta_1, \beta_2, \beta_3,$ and $\beta_5$ M1 served as null model. For $\\beta_4$ and $\\beta_6$, null model M1 and the alternative model switch roles in the reversed lineups, i.e. five plots show data simluated from the laternative model and only one plot shows data from M1.", label = "tab:experdetail", digits = c(0,0,0,3,4,3)), include.rownames=FALSE, 
      hline.after = c(-1,0,0,8,8,12))
@

@@

<<glmmres>>=
load("data/finalglmm31-2.RDA")
mod <- model2randomscalesize
res <- summary(mod)[[10]]
ests <- as.numeric(round(res[,1], 4))
oddsidx <- which(exp(ests) < .0001)
oddsidx2 <- which(exp(ests) > 1000000)
odds <- round(exp(ests), 4)
odds[oddsidx] <- "$<$0.0001"
odds[oddsidx2] <- "$>$1e+06"
se <- as.numeric(round(res[,2], 4))
pvalidx <- which(res[,4] < .0001)
pval <- sprintf("%.4f",round(res[,4],4))
pval[pvalidx] <- "$<$0.0001"
sigma_epsilon <- summary(model2randomscalesize)[[13]]$nick_name[[1]]
sigma_delta <- summary(model2randomscalesize)[[13]]$pic_id[[1]]
@

\npdecimalsign{.}
%\nprounddigits{3}

\begin{table}
\centering
\begin{tabular}{cn{5}{2}n{5}{3}rr}\hline
Parameter & \multicolumn{1}{r}{Estimate} & \multicolumn{1}{r}{Std Error} & $p$-value & Odds Multiplier \\ \hline\hline
$\alpha_{1+}$ & \Sexpr{ests[7]} & \Sexpr{se[7]} & \Sexpr{pval[7]} & \Sexpr{odds[7]} \\
$\alpha_{1-}$ & \Sexpr{ests[1]} & \Sexpr{se[1]} & \Sexpr{pval[1]} & \Sexpr{odds[1]}\\
$\beta_{1+}$ & \Sexpr{ests[19]} & \Sexpr{se[19]} & \Sexpr{pval[19]} & \Sexpr{odds[19]} \\
$\beta_{1-}$  & \Sexpr{ests[13]} & \Sexpr{se[13]} & \Sexpr{pval[13]} & \Sexpr{odds[13]} \\ \hline
$\alpha_{2+}$  & \Sexpr{ests[8]} & \Sexpr{se[8]} & \Sexpr{pval[8]} & \Sexpr{odds[8]} \\ 
$\alpha_{2-}$ & \Sexpr{ests[2]} & \Sexpr{se[2]} & \Sexpr{pval[2]} & \Sexpr{odds[2]} \\
$\beta_{2+}$ & \Sexpr{ests[20]} & \Sexpr{se[20]} & \Sexpr{pval[20]} & \Sexpr{odds[20]}  \\
$\beta_{2-}$   & \Sexpr{ests[14]} & \Sexpr{se[14]} & \Sexpr{pval[14]} & \Sexpr{odds[14]} \\ \hline
$\alpha_{3+}$ & \Sexpr{ests[9]} & \Sexpr{se[9]} & \Sexpr{pval[9]} & \Sexpr{odds[9]} \\
$\alpha_{3-}$ & \Sexpr{ests[3]} & \Sexpr{se[3]} & \Sexpr{pval[3]} & \Sexpr{odds[3]}  \\
$\beta_{3+}$ & \Sexpr{ests[21]} & \Sexpr{se[21]} & \Sexpr{pval[21]} & \Sexpr{odds[21]} \\ 
$\beta_{3-}$  & \Sexpr{ests[15]} & \Sexpr{se[15]} & \Sexpr{pval[15]} & \Sexpr{odds[15]} \\ \hline\hline
$\alpha_{5+}$  & \Sexpr{ests[11]} & \Sexpr{se[11]} & \Sexpr{pval[11]} & \Sexpr{odds[11]} \\
$\alpha_{5-}$ & \Sexpr{ests[5]} & \Sexpr{se[5]} & \Sexpr{pval[5]} & \Sexpr{odds[5]}  \\
$\beta_{5+}$ & \Sexpr{ests[23]} & \Sexpr{se[23]} & \Sexpr{pval[23]} & \Sexpr{odds[23]} \\
$\beta_{5-}$ & \Sexpr{ests[17]} & \Sexpr{se[17]} & \Sexpr{pval[17]} & \Sexpr{odds[17]} \\ \hline
$\alpha_{4+}$  & \Sexpr{ests[10]} & \Sexpr{se[10]} & \Sexpr{pval[10]} & \Sexpr{odds[10]} \\
$\alpha_{4-}$  & \Sexpr{ests[4]} & \Sexpr{se[4]} & \Sexpr{pval[4]} & \Sexpr{odds[4]} \\
$\beta_{4+}$ & \Sexpr{ests[22]} & \Sexpr{se[22]} & \Sexpr{pval[22]} & \Sexpr{odds[22]} \\
$\beta_{4-}$  & \Sexpr{ests[16]} & \Sexpr{se[16]} & \Sexpr{pval[16]} & \Sexpr{odds[16]} \\ \hline
$\alpha_{6+}$  & \Sexpr{ests[12]} & \Sexpr{se[12]} & \Sexpr{pval[12]} & \Sexpr{odds[12]} \\
$\alpha_{6-}$  & \Sexpr{ests[6]} & \Sexpr{se[6]} & \Sexpr{pval[6]} & \Sexpr{odds[6]} \\
$\beta_{6+}$ & \Sexpr{ests[24]} & \Sexpr{se[24]} & \Sexpr{pval[24]} & \Sexpr{odds[24]} \\ 
$\beta_{6-}$ & \Sexpr{ests[18]} & \Sexpr{se[18]} & \Sexpr{pval[18]} & \Sexpr{odds[18]} \\
\hline\hline
$\sigma^2_{\delta}$ & \Sexpr{round(sigma_delta, 4)} & \multicolumn{1}{r}{--} & -- & --\\
$\sigma^2_{\epsilon}$ &  \Sexpr{round(sigma_epsilon, 4)}  & \multicolumn{1}{r}{--} & -- & --\\
\hline 
\end{tabular}
\caption{\label{tab:glmmests}Summary of the results from fitting the model given in Equation~\ref{eq:glmm}}
\end{table}
